deconvolve: a protocol and R package for thermogravimetric decay curve deconvolution for lignocellulosic biomass trait calculation

### 2017-09-14 writing/draft.Rmd
writing updates

The Fraser-Suzuki function, due to its asymmetry, has been found to well predict kinetic curves and therefore be useful for deconvolution of parallel independent processes. The Fraser-Suzuki function is expressed as follows:

>>>>

The Fraser-Suzuki function, due to its asymmetry, is useful for predicting kinetic curves and therefore useful for the deconvolution of parallel independent processes. The Fraser-Suzuki function is expressed as follows:
